### 2015-02-15 Docs/visualization/visualization.tex
update some paths

\begin{figure}[t]
\centering
\includegraphics[height=0.4\textheight]{\visfigpath/plt00000_tfromp}
\caption[Basic plot of {\tt test2} done with {\tt plotsinglevar.py}]
{\label{fig:python} Plot of {\tt test2} done with the python
  script {\tt plotsinglevar.py}.}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[height=0.4\textheight]{\visfigpath/plt00000_tfromp_enucdot}
\caption[Plot of two variables from {\tt test2} done with {\tt plotsinglevar.py}]
{\label{fig:python_two} Plot of {\tt test2} done with the
  python script {\tt plotsinglevar.py} showing 2 variables plotted
  from a single plotfile.}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[height=0.4\textheight]{\visfigpath/plt00000_tfromp}
\caption[Basic plot of {\tt reacting\_bubble} done with {\tt plotsinglevar.py}]
{\label{fig:python} Plot of {\tt reacting\_bubble} done with the python
  script {\tt plotsinglevar.py}.}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[height=0.4\textheight]{\visfigpath/plt00000_tfromp_enucdot}
\caption[Plot of two variables from {\tt reacting\_bubble} done with {\tt plotsinglevar.py}]
{\label{fig:python_two} Plot of {\tt reacting\_bubble} done with the
  python script {\tt plotsinglevar.py} showing 2 variables plotted
  from a single plotfile.}
\end{figure}
